Making scalars work in \\Holographic Memories

### 2016-12-18 papers/hrr-paper/paper.tex

	% As a general rule, do not put math, special symbols or citations
	% in the abstract
	\begin{abstract}
		Vector Symbolic Architectures (VSAs) define a set of operations
		for association, (compressed) storage, manipulation and retrieval
		of symbolic concepts, represented as fixed-length vectors in
		${\rm I\!R}^n$.
		A subset of VSAs, Holographic Reduced Representations (HRRs),
		have proven to exhibit properties similar to human short-term
		memory and are, as such, interesting for computational modeling.

		In this paper we extend the HRR approach by introducing implicit,
		topology-preserving encoding/decoding procedures using radial
		basis functions.
		This involves randomly chosen permutations for encoding and
		their corresponding inverse for decoding. These are necessary
		for the uniform distribution of signals in Fourier space where
		embedding takes place.
		These novel encoding schemes, together with the extended operation
		pipeline, are akin to so-called \emph{clean-up modules after memory
		retrieval} (e.g., self-organizing maps). Effectively, encoding
		implicitly represents the symbol, so no further lookup is needed.

		We show that our encoding scheme does not have a negative impact
		on memory capacity in comparison to the original capacity
		benchmark for HRRs by Plate
		\cite{Plate:1995:HolographicReducedRepresentations}.
		We also evaluate our memories in different robotics tasks: top-down visual
		attention shift and state machine scripting (holographic
		controllers).
	\end{abstract}

@@

	In the case of lookup tables, in order to decode a specific symbolic vector, the elements from a symbol table are iterated over, the similarity to each of the entries is calculated and the symbol which presented maximum similarity is returned. With the help of a threshold for the similarity value false-positives can be excluded. A lookup requires O(n), where $n$ is the number of symbols known to the system. This approach works quite well for object identifiers (names), but has some non-desirable properties when used on scalar encoding. The space complexity will increase and may become infeasible, depending on the number of inputs needed. One way of handling symbolic scalar encoding is to discretize the whole input range into bins and assigning a random vector to each discrete value. This however may often prove to not satisfy the task needs any more.

@@

	\begin{figure}[th!]
		\center
		\begin{subfigure}{1.0\columnwidth}
			\center
			\includegraphics[width=0.6\columnwidth]{img/map_original.jpg}
			\caption{Original scene and a set of detected objects}
			\label{fig:object-detection}
		\end{subfigure}

		\begin{subfigure}{0.45\columnwidth}
			\center
			\includegraphics[width=\linewidth]{img/coord_example_1.png}
			\caption{Encoding of location (x,y) for "watch"}
			\label{fig:encoding-coord}
		\end{subfigure}
		\begin{subfigure}{0.45\columnwidth}
			\center
			\includegraphics[width=\linewidth]{img/coord_example_2.png}
			\caption{Encoding of the "watch" object ID as a randomly sampled vector}
			\label{fig:encoding-object}
		\end{subfigure}
				\begin{subfigure}{0.8\columnwidth}
					\center
					\includegraphics[width=0.8\linewidth]{img/coord_example_3.png}
					\caption{Representation of the complete visual scene, containing information about all 7 objects and their locations scrambled together}
					\label{fig:encoding-scene}
				\end{subfigure}

			\begin{subfigure}{0.45\columnwidth}
				\center
				\includegraphics[width=\linewidth]{img/probe_for_mug.png}
				\caption{Probing for "mug" returns location probability for a mug}
				\label{fig:probing-single}
			\end{subfigure}
			\begin{subfigure}{0.45\columnwidth}
				\center
				\includegraphics[width=\linewidth]{img/probe_for_pen.png}
				\caption{Probing for "pen" returns location probability with two areas.}
				\label{fig:probing-double}
			\end{subfigure}

>>>>

	% As a general rule, do not put math, special symbols or citations
	% in the abstract
	\begin{abstract}
		Vector Symbolic Architectures (VSAs) define a set of operations
		for association, (compressed) storage, manipulation and retrieval
		of symbolic concepts, represented as fixed-length vectors in
		${\rm I\!R}^n$.
		A subset of VSAs, Holographic Reduced Representations (HRRs),
		have proven to exhibit properties similar to human short-term
		memory and are, as such, interesting for computational modeling.
		In this paper we extend the HRR approach by introducing implicit,
		topology-preserving encoding and decoding procedures.
		We propose moving away from traditional exact symbolic representation
		to probabilistic one, replacing unique symbol identifiers with 
		probability density function.
		As we discover, this requires randomly chosen permutations for encoding and
		their corresponding inverse for decoding. These are necessary
		for the uniform distribution of signals across Fourier space where
		embedding takes place.
		These novel encoding schemes, together with the extended operation
		pipeline, are eliminating the need for so-called \emph{clean-up modules} after memory
		retrieval (e.g., self-organizing maps). Effectively, encoding
		implicitly represents the scalar symbol, so no further lookup is needed.
		We show that our encoding scheme has a positive impact
		on memory capacity in comparison to the original capacity
		benchmark for HRRs by Plate
		\cite{Plate:1995:HolographicReducedRepresentations}.
		We also evaluate our memories in two different robotics tasks: top-down visual
		attention shift and state machine scripting (holographic
		controllers).
	\end{abstract}

@@

	In the case of lookup tables, in order to decode a specific symbolic vector, the elements from a symbol table are iterated over, the similarity to each of the entries is calculated and the symbol which presented maximum similarity is returned. With the help of a threshold for the similarity value false-positives can be excluded. A lookup requires $O(n)$, where $n$ is the number of symbols known to the system. This approach works quite well for object identifiers (names), but has some non-desirable properties when used on scalar encoding. The space complexity will increase and may become infeasible, depending on the number of inputs needed. One way of handling symbolic scalar encoding is to discretize the whole input range into bins and assigning a random vector to each discrete value. This however may often prove to not satisfy the task needs any more.

@@

	\begin{figure}[th!]

		\begin{subfigure}{0.8\columnwidth}
			\center
			\includegraphics[width=0.8\linewidth]{img/coord_example_3.png}
			\caption{Representation of the complete visual scene, containing information about all 7 objects and their locations scrambled together}
			\label{fig:encoding-scene}
		\end{subfigure}

		\begin{subfigure}{0.45\columnwidth}
			\center
			\includegraphics[width=\linewidth]{img/probe_for_mug.png}
			\caption{Probing for "mug" returns location probability for a mug}
			\label{fig:probing-single}
		\end{subfigure}
		\begin{subfigure}{0.45\columnwidth}
			\center
			\includegraphics[width=\linewidth]{img/probe_for_pen.png}
			\caption{Probing for "pen" return mixture of Gaussian distributions}
			\label{fig:probing-double}
		\end{subfigure}
